---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Part 1

### Setup

* Overview different ways to
[setup](https://github.com/2DegreesInvesting/ds.terminal#setup) a terminal and
data.

### What is the terminal and why use it?

* It's one way to interact with a computer.
* They scale up much better than GUIs.
* It a common way to interact with cloud computing systems.

### Look and move around

```bash
# Print working directory
pwd

# List files and directories under the current working directory
ls

# Modify the output with flags. You may combine multiple flags
ls --all
ls -a

ls -al
ls -alt
ls -altr
ls -altrF

ls --help
```

Change to your home directory and explore it. This helps:

* Use autocomplete with Tab.
* Clear the terminal with clear (or ctrl + L).
* Reuse commands with Up/Down.

```{r}
cd ~
```

* Explore lesson's data under ~/Desktop recursively.

```bash
ls -R
```

Explore the directories `.` and `..`.

```bash 
ls -a
ls .
ls ..
```

Explore one linking/linked directory.

```bash
ls -l
ls R
ls /cloud/lib
```

These three commands return the same. Which one is wold you say is:

* default?
* relative?
* special?
* absolute?

```bash
ls
ls .
ls ~
ls /home/rstudio-user
```

These two commands return something different expect at `/`. Why?

```bash
ls .
ls ..

cd /
ls .
ls ..
```
